\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-08-02 ndss/intro.tex
minor

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

@@

\noindent\textbf{Summary.} To summarize the above five points, the novelty of \tool is in implementing cryptographic cost awareness inside a compiler, allowing the programmers to program in a high-level language absent of all the cryptographic details, while the compiler chooses the best circuit representation (boolean or arithmetic) for different parts of the program and also handles interconversions between them -- all this in a provably secure manner. Prior compilers such as Wysteria, ObliVM, and CBMC-GC use backends with single representations (either boolean or arithmetic), and so the  challenges associated with multiple representations and interconversions are absent. Moreover, as shown in Section~\sectionref{oblivm}, they perform poorly on ML tasks that involve a mix of arithmetic and boolean computations. The work of Kerschbaum {\em et al.}~\cite{autoS} integrates a backend with both boolean and arithmetic represenations. However it operates over circuits represented as a sequence of dyadic operations, while \tool provides a high-level programming language with loops and branches. \tool compilation is automatic and sub-quadratic in the size of generated ABY programs (e.g. \figureref{ex-aby}) after switching off memory safety checking. In sharp contrast, \cite{autoS} describes approaches that would be doubly exponential and exponential in the length of ABY programs. Finally, our partitioning technique, unlike prior work, which is specific to and works on Yao’s garbled circuits, works at the source level and is agnostic to the cryptographic backend.

>>>>

She can program the computation in one of the several programmer
friendly, domain-specific languages (such
as Fairplay~\cite{fairplay}, Wysteria~\cite{wysteria},
ObliVM~\cite{oblivm}, CBMC-GC~\cite{cbmcgc}, SMCL~\cite{smcl},
Sharemind~\cite{sharemind}, \cite{lambdaps} etc.) that would
automatically compile it to a \mpc protocol. However, all of these
frameworks use cryptographic backends that take as input
the computation expressed either as a boolean
circuit~(\cite{yao,gmw}) or as an arithmetic circuit~(\cite{sss,viff,gentry}). 
%
\dg{Do we want to say sharemind? It is only 3PC.}
%
The efficiency of the generated \mpc protocol is thus bounded by the
efficiency of representing the computation in \emph{one} of
these representations. For instance, multiplication of two
$\ell$-bit integers can either be expressed as a boolean circuit of
size $O(\ell^2)$, or as an arithmetic circuit with 1 multiplication
gate.
It is well-known that boolean circuits are not suitable for doing arithmetic operations such as integer multiplications but are unavoidable for boolean operations such as comparison \cite{aby,tasty,autoS,secureml,minionn,chameleon}.
%
For better efficiency, Alice would ideally like to compute
$w^Tx$ using an arithmetic circuit, and the comparison with $b$ using
a boolean circuit.
%

@@

\noindent\textbf{Summary.} To summarize the above five points, the novelty of \tool is in implementing cryptographic cost awareness inside a compiler, allowing the programmers to program in a high-level language absent of all the cryptographic details, while the compiler chooses the best circuit representation (boolean or arithmetic) for different parts of the program and also handles interconversions between them -- all this in a provably secure manner. Prior compilers such as Wysteria, ObliVM, and CBMC-GC use backends with single representations (either boolean or arithmetic), and so the  challenges associated with multiple representations and interconversions are absent. Moreover, as shown in \sectionref{oblivm}, they perform poorly on ML tasks that involve a mix of arithmetic and boolean computations. The work of Kerschbaum {\em et al.}~\cite{autoS} integrates a backend with both boolean and arithmetic represenations. However it operates over circuits represented as a sequence of dyadic operations, while \tool provides a high-level programming language with loops and branches. \tool compilation is automatic and sub-quadratic in the size of generated ABY programs (e.g. \figureref{ex-aby}) after switching off memory safety checking. In sharp contrast, \cite{autoS} describes approaches that would be doubly exponential and exponential in the length of ABY programs. Finally, our partitioning technique, unlike prior work, which is specific to and works on Yao’s garbled circuits, works at the source level and is agnostic to the cryptographic backend.
